---
title: "NewYork Evictions"
author: "tangzhixian"
date: "2024-11-28"
output: html_document
---


introduction:
Evictions in urban areas like New York City are a critical issue, reflecting economic stress, housing insecurity, and systemic inequalities. In response to these challenges, the present study examines the spatial and contextual dimensions of eviction data from 2020. This analysis aims to identify patterns and underlying factors that contribute to evictions, thereby providing actionable insights for policymakers to mitigate the issue and support at-risk communities.
```{r}
library(spatstat)
library(here)
library(sp)
library(tmap)
library(tmaptools)
library(janitor)
library(sf)
library(tidyverse)
library(spdep)
library(RColorBrewer)
library(dplyr)
```
```{r}
NewYork_Districts <- st_read("/Users/tangzhixian/Desktop/practical homework/Community Districts/geo_export_f2908129-86cd-4024-a697-4a627538a408.shp")
NewYork_Evictions <- read_csv("/Users/tangzhixian/Desktop/practical homework/Evictions_20241110.csv")
```
```{r}
NewYork_Evictions_2020 <- NewYork_Evictions %>%
  mutate(`Executed Date` = as.Date(`Executed Date`, format = "%m/%d/%Y")) %>%
  filter(format(`Executed Date`, "%Y") == "2020")
## Remove missing values and convert to sf objects
NewYork_Evictions_2020 <- NewYork_Evictions_2020[!is.na(NewYork_Evictions_2020$Longitude) & !is.na(NewYork_Evictions_2020$Latitude), ]
NewYork_Evictions_transformed <- st_as_sf(NewYork_Evictions_2020, 
                                 coords = c("Longitude", "Latitude"), 
                                 crs = 4326)
NewYork_Evictions_sf <- st_transform(NewYork_Evictions_transformed, crs = 2263)
NewYork_Districts <- st_transform(NewYork_Districts, st_crs(NewYork_Evictions_sf))
df_2020 <- NewYork_Evictions %>%
  mutate(`Executed Date` = as.Date(`Executed Date`, format = "%m/%d/%Y")) %>%
  filter(format(`Executed Date`, "%Y") == "2020")

```
```{r}
tm_shape(NewYork_Districts) + 
  tm_polygons(col = NA, alpha = 0.5) +  
  tm_shape(NewYork_Evictions_sf) +
 tm_dots(col = "blue", size = 0.001) 
```
```{r}
##data cleaning 
NewYork_Evictions_sf <- distinct(NewYork_Evictions_sf)
```
```{r}
# Spatial subsetting
NewYork_Evictions_sfSub <- NewYork_Evictions_sf[NewYork_Districts,]
#check to see that they've been removed
tmap_mode("plot")
tm_shape(NewYork_Districts) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(NewYork_Evictions_sfSub) +
  tm_dots(col = "blue", size = 0.001)
#identify points
intersect_indices <-st_intersects(NewYork_Districts, NewYork_Evictions_sfSub)
```

```{r}
window <- as.owin(NewYork_Districts)
plot(window)

NewYork_Evictions_sfSub<- NewYork_Evictions_sfSub %>%
  as(., 'Spatial')
#create a ppp object
NewYork_Evictions_sfSub.ppp <- ppp(x=NewYork_Evictions_sfSub@coords[,1],
                          y=NewYork_Evictions_sfSub@coords[,2],
                          window=window)

## Kernel Density Estimation
NewYork_Evictions_sfSub.ppp %>%
  density(., sigma=1000) %>%
  plot()
```

```{r}
## Quadrat Analysis
plot(NewYork_Evictions_sfSub.ppp,
     pch=16,
     cex=0.5, 
     main="Evictions in NewYork")

#now count the points in that fall in a 6 x 6
#grid overlaid across the windowBluePlaquesSub.ppp2<-BluePlaquesSub.ppp %>%
NewYork_Evictions_sfSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6)%>%
    plot(., add=T, col="red")

```

```{r}
## #run the quadrat count
Qcount <- NewYork_Evictions_sfSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6) %>%
  as.data.frame() %>%
  dplyr::count(Var1=Freq)%>%
  dplyr::rename(Freqquadratcount=n)

Qcount %>% 
  summarise_all(class)
```

```{r}
sums <- Qcount %>%
  #calculate the total blue plaques (Var * Freq)
  mutate(total = Var1 * Freqquadratcount) %>%
  dplyr::summarise(across(everything(), sum))%>%
  dplyr::select(-Var1) 

lambda<- Qcount%>%
  #calculate lambda
  mutate(total = Var1 * Freqquadratcount)%>%
  dplyr::summarise(across(everything(), sum)) %>%
  mutate(lambda=total/Freqquadratcount) %>%
  dplyr::select(lambda)%>%
  pull(lambda)

```



```{r}
plot(NewYork_Evictions_sfSub.ppp,
     pch=16,
     cex=0.5, 
     main="Evictions in NewYork")

#now count the points in that fall in a 6 x 6
#grid overlaid across the windowBluePlaquesSub.ppp2<-BluePlaquesSub.ppp %>%
NewYork_Evictions_sfSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6)%>%
    plot(., add=T, col="red")
```
```{r}
Qcount <- NewYork_Evictions_sfSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6) %>%
  as.data.frame() %>%
  dplyr::count(Var1=Freq)%>%
  dplyr::rename(Freqquadratcount=n)

Qcount %>% 
  summarise_all(class)
```
```{r}
sums <- Qcount %>%
  #calculate the total blue plaques (Var * Freq)
  mutate(total = Var1 * Freqquadratcount) %>%
  dplyr::summarise(across(everything(), sum))%>%
  dplyr::select(-Var1) 

lambda<- Qcount%>%
  #calculate lambda
  mutate(total = Var1 * Freqquadratcount)%>%
  dplyr::summarise(across(everything(), sum)) %>%
  mutate(lambda=total/Freqquadratcount) %>%
  dplyr::select(lambda)%>%
  pull(lambda)
```
```{r}
QCountTable <- Qcount %>%
  mutate(Pr=((lambda^Var1)*exp(-lambda))/factorial(Var1))%>%
  #now calculate the expected counts based on our total number of plaques
  #and save them to the table
  mutate(Expected= (round(Pr * sums$Freqquadratcount, 0)))

#Compare the frequency distributions of the observed and expected point patterns
plot(c(1,5),c(0,14), type="n",
xlab="Number of Blue Plaques (Red=Observed,Blue=Expected)", 
     ylab="Frequency of Occurances")
points(QCountTable$Freqquadratcount, 
       col="Red", 
       type="o", 
       lwd=3)
points(QCountTable$Expected, col="Blue", 
       type="o", 
       lwd=3)
```
```{r}
#！！！！！
teststats <- quadrat.test(NewYork_Evictions_sfSub.ppp, nx = 6, ny = 6)

plot(NewYork_Evictions_sfSub.ppp,pch=16,cex=0.5, main="Blue Plaques in Harrow")
plot(teststats, add=T, col = "red")
```



```{r}
# Ripley’s K  为什么画不全
K <- NewYork_Evictions_sfSub.ppp %>%
  Kest(., correction="border") %>%
  plot()
Kval <- as.data.frame(Kest(NewYork_Evictions_sfSub.ppp, correction = "Ripley"))
```

```{r}
library(fpc)
st_geometry(BoroughMap)
```

















```{r}
library(sf)
points_sf_joined <- NewYork_Districts%>%
  mutate(n = lengths(st_intersects(., NewYork_Evictions_sfSub)))%>%
  janitor::clean_names()%>%
  #calculate area
  mutate(area=st_area(.))%>%
  #then density of the points per ward
  mutate(density=n/area)%>%
  #select density and some other variables 
  dplyr::select(density, boro_cd, n,geometry)

points_sf_joined<- points_sf_joined %>%                    
  group_by(geometry) %>%         
  summarise(density = first(density),
          wardname= first(boro_cd),
          plaquecount= first(n))

tm_shape(points_sf_joined) +
    tm_polygons("density",
        style="jenks",
        palette="PuOr",
        midpoint=NA,
        popup.vars=c("boro_cd", "density"),
        title="NewYork_Evictions density")
```
```{r}
# calculate the centroids of all Wards in London
coordsW <- points_sf_joined%>%
  st_centroid()%>%
  st_geometry()
  
plot(coordsW,axes=TRUE)

# create a neighbours list
LWard_nb <- points_sf_joined %>%
  poly2nb(., queen=T)
summary(LWard_nb)
## plot map
plot(LWard_nb, st_geometry(coordsW), col="red")
#add a map underneath
plot(points_sf_joined$geometry, add=T)

```
```{r}
# Moran’s I
Lward.lw <- LWard_nb %>%
  nb2listw(., style="C")

I_LWard_Global_Density <- points_sf_joined %>%
  pull(density) %>%
  as.vector()%>%
  moran.test(., Lward.lw)

I_LWard_Global_Density
```
```{r}
# Geary’s C
C_LWard_Global_Density <- 
  points_sf_joined %>%
  pull(density) %>%
  as.vector()%>%
  geary.test(., Lward.lw)

C_LWard_Global_Density
```


```{r}
# Getis Ord
G_LWard_Global_Density <- 
  points_sf_joined %>%
  pull(density) %>%
  as.vector()%>%
  globalG.test(., Lward.lw)

G_LWard_Global_Density
```

```{r}
# Local Moran’s I
I_LWard_Local_count <- points_sf_joined %>%
  pull(plaquecount) %>%
  as.vector()%>%
  localmoran(., Lward.lw)%>%
  as_tibble()

I_LWard_Local_Density <- points_sf_joined %>%
  pull(density) %>%
  as.vector()%>%
  localmoran(., Lward.lw)%>%
  as_tibble()

# output the localMoran object
slice_head(I_LWard_Local_Density, n=5)

# Add the local Moran index to our table
points_sf_joined <- points_sf_joined %>%
  mutate(plaque_count_I = as.numeric(I_LWard_Local_count$Ii))%>%
  mutate(plaque_count_Iz =as.numeric(I_LWard_Local_count$Z.Ii))%>%
  mutate(density_I =as.numeric(I_LWard_Local_Density$Ii))%>%
  mutate(density_Iz =as.numeric(I_LWard_Local_Density$Z.Ii))
```

```{r}
# plot localMoran map
breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)

MoranColours<- rev(brewer.pal(8, "RdGy"))

tm_shape(points_sf_joined) +
    tm_polygons("plaque_count_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title="Local Moran's I, Evictions in NewYork")
```


Local Getis Ord
```{r}
Gi_LWard_Local_Density <- points_sf_joined %>%
  pull(density) %>%
  as.vector()%>%
  localG(., Lward.lw)

head(Gi_LWard_Local_Density)
```
```{r}
points_sf_joined <- points_sf_joined %>%
  mutate(density_G = as.numeric(Gi_LWard_Local_Density))

GIColours<- rev(brewer.pal(8, "RdBu"))

#now plot on an interactive map
tm_shape(points_sf_joined) +
    tm_polygons("density_G",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title="Gi*, Evictions in NewYork")
```








